Robustness of MinD oscillation in \emph{Escherichia coli} with diverse cell shapes

### 2014-11-07 paper/paper-MinD.tex
edits of conclusions Tested everything on bennet.

In contrast to the stochastic model, the original deterministic
version of the model~\cite{huang2003dynamic} predicts behavior that
contradicts experimental observations, namely robust and periodic
bipolar oscillation in irregularly shaped cells, with a minor
intermediate maximum appearing in shape \emph{B}.  Thus we conclude
that this method is inconsistent with experiment, and cannot be relied
upon for predictions of the behavior of the MinD system.  This is the
most clear example of the inadequacy of the deterministic simulation
method in reproducing experimental behavoir of the MinD system to
date.  Until now the results of deterministic and stochastic
simulation have largely coincided, with the stochastic method showing
minor differences in behavoir when compared to deterministic
models~\cite{kerr2006division, fange2006noise, huang2004min,
  kruse2007experimentalist}.

We find that flattened but regular and symmetric cells exhibit MinD
oscillations that are qualitatively similar to the oscillations
observed experimentally (and in our simulation) in irregular and
asymmetric cells.  This demonstrates that asymmetry is not required in
order to induce spatially irregular MinD oscillations.  In addition,
the temporal regularity of oscillations is only moderately affected by
irregularity in the shape of flattened cells.  Thus we conclude
that it is the flattening of the cells rather than their irregular
shape that primarily causes the spatial irregularity of maxima which
is observed by Mannik \emph{et al.}~\cite{mannik2012robustness}.

>>>>

In contrast to the stochastic model, the original deterministic
version of the model~\cite{huang2003dynamic} predicts behavior that
contradicts experimental observations.  Specifically, the
deterministic model predicts robust and periodic bipolar oscillation
in irregularly shaped cells, with a minor intermediate maximum
appearing in shape \emph{B}.  Thus we conclude that this method is
inconsistent with experiment, and cannot be relied upon for
predictions of the behavior of the MinD system.  This is the most
clear example of the inadequacy of the deterministic simulation method
in reproducing experimental behavoir of the MinD system to date.
Until now the results of deterministic and stochastic simulation have
largely coincided, with the stochastic method showing minor
differences in behavoir when compared to deterministic
models~\cite{kerr2006division, fange2006noise, huang2004min,
  kruse2007experimentalist}.

We find that flattened but regular and symmetric cells exhibit MinD
oscillations that are qualitatively similar to the oscillations
observed experimentally (and in our simulation) in irregular and
asymmetric cells.  This demonstrates that asymmetry is not required in
order to induce spatially irregular MinD oscillations.  In addition,
the temporal regularity of oscillations is only moderately affected by
irregularity in the shape of flattened cells.  Thus we conclude that
it is the flattening of the cells rather than their irregular shape
that primarily causes the disruption of regular bipolar oscillation
which is observed by Mannik \emph{et al.}~\cite{mannik2012robustness}.
